---
title: "Homework: Reproducibility and Professional Communication"
execute:
  error: true
author: "Thu Dang"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
```


# Reproducible Examples & Debugging

In the following examples, evaluate each problem using the criteria of a minimal reproducible example from [this StackOverflow post](https://stackoverflow.com/help/minimal-reproducible-example). 

Specifically, address the following things: 

1. Are the question and problem description complete?

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

3. Is the example minimal? Does it include extra code or information that is not necessary?

4. Does the question describe any attempted solutions?


Then, using what you know about R and Python, try to debug the problem using the strategies in [the debugging chapter](https://srvanderplas.github.io/stat-computing-r-python/part-gen-prog/06-debugging.html). Once you are thoroughly stumped, or you believe you have solved the problem, compare your solutions to those given on StackOverflow using the link.

## Why Doesn't this R function work?

> I created the following function to append new strings on a vector of strings called "meals". However, when I use this function to append an string input into my "meals" vector, it does not work.

```
 add <- function(str) {
      meals <- append(meals, as.character(str))  
    }
```

[Link](https://stackoverflow.com/questions/39795961/why-doesnt-this-r-function-work?noredirect=1&lq=1) to original SO post. 


---

1. Are the question and problem description complete?

Not fully. It doesn't show how the meals vector was created or what output was expected. There is also no information about any error messages. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

The issue is kind of reproducible but but I need more information. It would help if they showed how they defined meals, how they called the function and what error they get. 

3. Is the example minimal? Does it include extra code or information that is not necessary?

It is too minimal. It doesn't include important details about where the meals variable comes from and and what the function should return.

4. Does the question describe any attempted solutions?

No, they didn't show any attempted solutions. 

*My debugging:* The problem is that meals doesn't exist inside the function. And the function doesn't return anything, so nothing changes after calling it. The function should be like:

```
 add <- function(meals, str) {
      meals <- append(meals, as.character(str))  
    }
meals <- "banh mi"
meals <- add(meals, "pho")
meals
```

## Function not working R

> I've never programmed before and am trying to learn. I'm following that "coursera" course that I've seen other people post about — a course offered by Johns Hopkins on R programming.

> Anyway, this was supposed to be my first function. Yet, it doesn't work! But when I type out all the steps individually, it runs just fine... Can anyone tell me why?

```
pollutantmean <- function(directory, pollutant, id = 1:332){
    x<- list.files("/Users/mike******/Desktop/directory", full.names=TRUE)
    y<- lapply(x, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA
Warning message:
In mean.default(z$pollutant, na.rm = TRUE) :
  argument is not numeric or logical: returning NA

####

x<- list.files("/Users/mike******/Desktop/specdata",full.names=TRUE)
y<- lapply(x,read.csv)
z<- do.call(rbind.data.frame,y[1:10])
mean(z$nitrate,na.rm=TRUE)
[1] 0.7976266
```


[Link](https://stackoverflow.com/questions/24123224/function-not-working-r/24141502)


---

1. Are the question and problem description complete?

 Mostly complete. They show the full code and shows the error message. They also showed the version that works when they run it step by step. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

Yes, they give enough information. I can improve the code by using the real argument directory instead of a hard-coded path. The function call should also pass "nitrate" and "sulfate" as strings, not as variables.

3. Is the example minimal? Does it include extra code or information that is not necessary?

Mostly minimal, but there is some extra code and the wrong use of the pollutant argument. It should not use z$pollutant directly. 

4. Does the question describe any attempted solutions?

Yes, they tried running the code step by step.

*My debugging:* The issue is using z$pollutant instead of z[[pollutant]]. And the function ignores the argument directory and uses the literal string directory. Moreover, pollutant should be used as a string.

```
pollutantmean <- function(directory, pollutant, id = 1:332){
    x <- list.files(directory, full.names = TRUE)
    y <- lapply(x[id], read.csv)
    z <- do.call(rbind, y)

    mean(z[[pollutant]], na.rm = TRUE)
}

pollutantmean("specdata", "nitrate", 1:10)
```

## Inexplicable error when trying to export my R notebook

> Getting this error from R Markdown when trying to export my .RMD

```
"Error in filter(Gastropods, Species == "Cellana") :  object 'Species' not found Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> filter"
```

> However, all my plots are coming out successfully. I can clearly see in the data that the species column is there and that Cellana is a species. No spelling errors or anything.

> My first 20 or so lines of code are below (between the ### symbols)


````{r echo=FALSE}
cat(paste(readLines("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt"), collapse = '\n'))
````

You can find this sample file [here](https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt)


[Link](https://stackoverflow.com/questions/44193367/inexplicable-error-when-trying-to-export-my-r-notebook)

---

1. Are the question and problem description complete?

Mostly complete. They show the error and mentions column Species exists, but doesn’t share enough code to recreate the problem. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

Yes but not fully. The error happened when knitting an R Markdown file, because the R session during knitting is clean. To make it reproducible, they could show how they read the data and which packages were loaded. 

3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, but they pasted too many lines of code that are not directly relating to the error. 

4. Does the question describe any attempted solutions?

No. They only showed “No spelling errors,” but didn’t show what they already tried. 

*My debugging:* The error says "object 'Species' not found" even though they can see it in their data. This might be they didn't create the data Gastropods before calling filter(), or they didn't load library(dplyr) in the R Markdown.

````{r echo=FALSE}
library(dplyr)
Gastropods <- read.csv("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt")
filter(Gastropods, Species == "Cellana")
````

## Python if elif else statement

> I'm trying to create a program with python that calculate the cost for shipping.

> However, I can't run the program to where it works properly.

> What ever my total is the same amount comes out as $6 for US and $8 for Canada. I can't seem to get pass that.

> Example:

```
total = raw_input('What is the total amount for your online shopping?')
country = raw_input('Shipping within the US or Canada?')

if country == "US":
    if total <= "50":
        print "Shipping Costs $6.00"
    elif total <= "100":
            print "Shipping Costs $9.00"
    elif total <= "150":
            print "Shipping Costs $12.00"
    else:
        print "FREE"

if country == "Canada":
    if total <= "50":
        print "Shipping Costs $8.00"
    elif total <= "100":
        print "Shipping Costs $12.00"
    elif total <= "150":
        print "Shipping Costs $15.00"
    else:
        print "FREE"
```


[Link](https://stackoverflow.com/questions/19371643/python-if-elif-else-statement)

---

1. Are the question and problem description complete?

Yes, they clearly explain the problem. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

Yes, it is very easy to reproduce because the code runs but gives wrong results. 

3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, it only contains what is needed to show the problem. 

4. Does the question describe any attempted solutions?

No, they didn't mention anything. 

*My debugging:* The problem is comparing strings instead of numbers. raw_input() returns text, so 50 is like text, not a number. We need to convert it to a float before comparing.

```
total = float(raw_input('What is the total amount for your online shopping?'))
```

# Professional Communication

## Slides

*I created a Quarto slide file slides.qmd with two output formats: reveal.js (HTML) and beamer (PDF).
I used Overleaf's template to create my CV and then I compiled it to cv.pdf file.*

Create a set of quarto slides in the file slides.qmd. 

Set two different output formats - for instance, reveal.js and beamer. 

In your slides:

- Introduce yourself and show a picture of yourself
- Provide basic biographical information: birthday, where you grew up
- Show a picture of your favorite animal
- Provide your favorite plot, generated in either R or python. (This can be one you've generated in this class). Ensure that the code does not show, but the plot does.
- Provide a link to your CV, which you will generate in the next part.

## CV

Select a CV template that uses either LaTeX or Markdown:

- https://github.com/kazuyanagimoto/quarto-awesomecv-typst
- https://github.com/schochastics/quarto-cv
- https://www.overleaf.com/latex/templates/tagged/cv

Use the template to create a curriculum vitae that has your education, work experience, and any other sections you would like to include. Compile your CV and link to it in your slides. 

